\LARGE \bf Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty [v7 Feb 18, 2015 ]

### 2015-03-11 paper.tex
changed monte-carlo to uniform

\begin{abstract}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities. 
Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
We compare against Monte-Carlo sampling and an adaptive sampling approach, that reduces the set based on a current estimate of sample mean,previously proposed for grasping planar objects under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
\end{abstract}

@@

We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against Monte-Carlo integration and an adaptive sampling method, which reduced the set size based on sample mean, proposed by Kehoe et al. \cite{kehoe2012toward}. In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}.
In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean adaptive sampling approach previously used .

@@

Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
It can be computationally expensive though to sample all proposed grasps to convergence.
To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure, which tries to avoid sampling grasps that seem to have lower quality based on past observation. 
However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.

@@

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We initialize all algorithms by sampling each grasp 1 time. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration). We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation. The adaptive sampling method of Kehoe et al. prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.

\todo{THis might still be vague} For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and show the grasps selected for three randomly selected objects for the tried methods in Fig. \ref{fig:shape_samples}. Interestingly in Fig. \ref{fig:grasp_quality}, Gittins and Thompson select a stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .

 In Fig. \ref{fig:pulls_per_grasp}, we plot samples per grasp quality. Gittins and Thompson appear to allocate  more samples to grasps of high quality. In contrast to Monte-Carlo, which uniformly allocate grasp samples. The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.23$\%$ of total samples. Monte-Carlo sampling and the adaptive sampling method allocate $0.01\%$  and $0.06\%$ of total samples, respectively.

 The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq. \ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$. We plot the confidence intervals around the return grasp vs. the number of samples drawn in Fig. \ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling. \todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods. This can be explained by the fact that in our experiments the MAB algorithms allocate more samples on average to grasp returned at each iteration, which is illustrated in Fig. \ref{fig:pulls_per_grasp}.

@@

Assessing grasp quality under  uncertainty can be computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
A key insight from our work is that uniformly allocating samples to grasps is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time. Initial results have shown our MAB approach to outperform the methods of prior work, Monte-Carlo sampling and the adaptive sampling approach proposed by Kehoe et al. \cite{kehoe2012estimating} in terms of finding a higher quality grasp faster. 
 However, as shown in Fig. \ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps. Fortunately, though these cases occur with a small very probability, however it is important for a practitioner to be aware of them.

As we scale to larger 3D objects the possible number of grasp candidates will be substantially larger, the more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}. The MAB algorithms presented above assumed that each option is independent. In the grasping context though spatial information about grasps could provide information about the quality of similar grasps. We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we have to find an appropriate feature representation for a grasp, which is an exciting project for on going work. 
\bibliographystyle{IEEEtranS}
\bibliography{references}

>>>>

\begin{abstract}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities. 
Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
We compare against two previously proposed methods for grasp selection uniform allocation, or uniformly selecting samples, and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps. We  consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
\end{abstract}

@@

We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation, or randomely sampling grasps, and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al. \cite{kehoe2012toward}. In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}.
In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean adaptive sampling approach previously used .

@@

Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
It can be computationally expensive though to sample all proposed grasps to convergence.
To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which at a set iteration discards a subset of the grasps that seem unlikely to be of high quality . However, the method pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.

@@

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We initialize all algorithms by sampling each grasp 1 time. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Iterative Pruning \cite{kehoe2012toward} and uniform allocation). Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information. Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation.

\todo{This might still be vague} As illustrated in Fig. \ref{fig:grasp_quality}, Gittins and Thompson select a grasp at stopping time $T_s$ that on average has a higher probability of force closure than uniform allocation and Iterative Pruning . For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and for each method visualize the grasp selected in Fig. \ref{fig:shape_samples}.

 The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq. \ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$. We plot the confidence intervals around the return grasp vs. the number of samples drawn in Fig. \ref{fig:confidence} for Thompson Sampling, Iterative Pruning\cite{kehoe2012toward} and uniform allocation. \todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.

 In Fig. \ref{fig:pulls_per_grasp}, we plot samples per grasp quality. Gittins and Thompson appear to allocate  more samples to grasps of high quality in contrast to uniform allocation and Iterative Pruning. The ability to find grasps with a higher probability of force  faster and have a smaller confidence interval on the returned quantity can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples. Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.

@@

Assessing grasp quality under  uncertainty can be computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time. Initial results have shown our MAB approach to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster. 
 However, as shown in Fig. \ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps. Fortunately, though these cases occur with a small very probability, however it is important for a practitioner to be aware of them.

As we scale to 3D objects the possible number of grasp candidates will be substantially larger. The more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}. However, the MAB algorithms presented above assumed that each option is independent. In the grasping context though spatial information about grasps could provide information about the quality of similar grasps. We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we would have to find an appropriate feature representation for a grasp that can accurately represent this. Learning these features and applying these to MAB methods will be an exciting project for future work. 
\bibliographystyle{IEEEtranS}
\bibliography{references}
